### 2017-09-09 paper/evaluation.tex
pass on survey

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.   The result set is sorted
in descending order of stars.

\vspace{1ex}
\begin{figure}[t!]
\centering
\scriptsize
\lstset{
  escapeinside={@}{@},
  numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
  basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
  deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
 +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
\end{lstlisting}
  \caption{\label{fig:subject-query} Query to the \github{} API for
  projects that (1) use Java, (2) contains at least 100
  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
  the string \emph{mvn} in the \emph{readme} file.}
  \vspace{-5ex}  
\end{figure}

We used the following methodology to select projects for
analysis. After obtaining the list of potential projects from GitHub, we filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and nondeterministic results observed from sequential executions.
As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
  \vspace{-1ex}
\end{figure}

%\subsection{Setup and Replication}
\label{sec:setup}

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  We used\Comment{ Git,} Java 8 and Maven
3.3.9 to build projects and run test suites. To
process test results and generate plots
we used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are
publicly available for replication on our website~\cite{ourwebpage}.
This includes supporting scripts\Comment{ (\eg, the scripts to run the tests
and generate raw analysis data)} and the full list of projects.

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails, containing the survey, to those developers.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

>>>>

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
in the dir structure (\eg{}, \emph{pom.xml}).
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

\vspace{1ex}
\begin{figure}[h!]
\centering
\scriptsize
\lstset{
  escapeinside={@}{@},
  numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
  basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
  deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016+mvn%20in:readme
        &sort=stars
\end{lstlisting}
  \caption{\label{fig:subject-query} Query to the \github{} API for
  projects with the following criteria: (1) Java, (2) at least 100
  stars, (3) updated on January 1st, 2016 (or later), (4) contains
  the string \emph{mvn} in the \emph{readme} file. Output is
  paginated in descending order of stars.}
\end{figure}

After obtaining a list of potential projects, we filtered those
containing a \pomf{} file in the root directory.  A Maven project may
contain several sub-modules with multiple \pomf{} files.
To avoid introducing noise in our experiments, for each project, we
executed the tests \SubjectsReruns{} times to filter projects with
deterministic outcome.
As of August 25th 2017, our search criteria returned \SubjectsGithub{}
subjects.

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, and we were unable to test
\SubjectsGithubNotTestable{} projects  due to incompatible environment
(\eg, missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
``flaky tests''~\cite{luo-etal-fse2014}.
In general, a ``flaky test'' is a test that either pass or fail under
the same circumstances leading to non-deterministic results.
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.
We ignored failing tests with JUnit's
\CodeIn{@Ignore} annotation on the remaining projects.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
  \vspace{-2ex}
\end{figure}

\subsection{Setup and Replication}
\label{sec:setup}

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include Git, Java 8, and Maven
3.3.9.
We used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to
process test results and generate plots.  All source artifacts are
publicly available for replication on our website~\cite{ourwebpage}.
This includes supporting scripts (\eg, the script that test subjects
and generates raw analysis data) and the full list of projects.

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails, containing the survey, to those developers.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies. \Luis{In one specific case, one developer worked in
  multiple projects, and we consider it as a different answer.}
Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:
